### 2018-02-01 includes/appendix.tex
Finished Reverse.

The restriction that \texttt{Translate} must fix the digit characters can be
relaxed if we are translaing problem instances that do not use
\texttt{str.to.int} or \texttt{str.from.int}.

>>>>

The restriction that \textit{Translate} must fix the digit characters can be
relaxed if we are translating problem instances that do not use
\texttt{str.to.int} or \texttt{str.from.int}. Without these operators we can
show $\textit{Translate}(\eval (e)) = \eval (\textit{Translate}(e))$ directly by
induction without having to worry about fixing digits pointwise.

\subsection{Reverse}
\textit{Reverse} does not transform programs that use \texttt{str.replace},
\texttt{str.indexof}, \texttt{str.to.int}, and \texttt{str.from.int}. These
operators do not have a well-defined notion of a reverse. The required lemma is
proved by induction on the rest of the operators similar to proof for
\textit{Translate}.

We end our discussion on \textit{Reverse} by nothing that although it disallowed
\texttt{str.replace} only because it didn't have a natural notion of a reverse
in the theory we were working with. If we expand our theory to also include an
operator that replaces the last instance, we can transform problems that include
\texttt{str.replace}.
